```{r global_options, include=FALSE}
require(knitr)
require(plyr)
require(xtable)
require(googleVis)
require(rCharts)
opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
```

---
title: "Kanban Metrics"
author: "Steve Bargelt"
date: "`r format(Sys.Date(), "%A, %B %d, %Y")`"
output: html_document
---

```{r, echo=FALSE }
initial.dir <- getwd()
#setwd("C:/Users/bargels/code/kanbanStats")
classes <- c(Opened="Date", Closed="Date", Ready.for.Dev.Date="Date", Due.Date="Date")
kanban <- read.csv("data/KanbanScrubbed.csv", header=TRUE, colClasses=classes)
kanban2013 <- read.csv("data/Kanban2013Scrubbed.csv", header=TRUE)

#kanban <- rbind(kanban, kanban2013)
kanban2013 <- NULL

#kanban.all <- subset(kanban, !is.na(kanban$Closed))

kanban$LeadTime <- apply(kanban[c('Closed', 'Opened')], 1, 
                         function(x) as.Date(x[1],format='%Y-%m-%d') - 
                           as.Date(x[2],format='%Y-%m-%d'))

kanban$CycleTime <- apply(kanban[c('Closed', 'Ready.for.Dev.Date')], 1, 
                          function(x) as.Date(x[1],format='%Y-%m-%d') - 
                            as.Date(x[2],format='%Y-%m-%d'))



kanban$Quarter = quarters(as.Date(kanban$Closed))
kanban$Month = as.numeric(strftime(kanban$Closed, "%m"))
kanban$Day = as.numeric(strftime(kanban$Closed, "%d"))
kanban$Year = as.numeric(strftime(kanban$Closed, "%Y"))

kanban.features <- subset(kanban, kanban$Type == "Feature")
kanban.bugs <- subset(kanban, kanban$Type == "Bug")

##library(datasets)
##s <-- split(airquality, airquality$month)
##lapply(s, function(x) colMeans(x[, c("Ozone', "Solar.R", "Wind")]))
##sapply(s, function(x) colMeans(x[, c("Ozone', "Solar.R", "Wind")]))
##sapply(s, function(x) colMeans(x[, c("Ozone', "Solar.R", "Wind")], na.rm=TRUE))
```
## Dashboard


```{r, results='asis'}

featurecountbyquarter <- count(kanban.features, c('Year','Quarter'))

featuretimesbyquarter <- 
    aggregate(kanban.features[,11:12], 
              list(kanban.features$Quarter, kanban.features$Year), 
              mean, na.rm=TRUE)
colnames(featuretimesbyquarter) <- c("Quarter", "Year", "LeadTime", "CycleTime")

featuresbyquarter <- 
    merge(featurecountbyquarter, featuretimesbyquarter, 
          by = c("Quarter", "Year"))
colnames(featuresbyquarter) <- c("Quarter", "Year", "Count", "LeadTime", "CycleTime")

featurecountbyquarter <- NULL
featuretimesbyquarter <- NULL

testTable <- gvisTable(subset(featuresbyquarter, featuresbyquarter$Year == "2014"),options=list(width=800))
plot(testTable)

testTable <- gvisTable(subset(featuresbyquarter, featuresbyquarter$Year == "2013"),options=list(width=800))
plot(testTable)

 timesbymonth <- 
     aggregate(kanban.features[,11:12], 
               list(kanban.features$Month, kanban.features$Year), 
               mean, na.rm=TRUE)

 timesbyQuarter <- 
     aggregate(kanban.features[,11:12], 
               list(kanban.features$Quarter, kanban.features$Year), 
               mean, na.rm=TRUE)

```
## Testing GoogleVis

```{r, results='asis'}
# op <- options(gvis.plot.tag = "chart")
# 
# Line <- gvisLineChart(kanban.features, xvar="Closed", yvar=c("LeadTime", "CycleTime"))
# plot(Line)
# 
# Line <- gvisLineChart(timesbymonth, xvar="Group.1", yvar=c("LeadTime", "CycleTime"))
# plot(Line)
# 
# ## M <- gvisMotionChart(timesbymonth, 'LeadTime', 'Year',
# ##       options=list(width=400, height=350))
# ## plot(M)

```
## Testing rCharts

```{r, results='asis'}

# hair_eye_male <- subset(as.data.frame(HairEyeColor), Sex == "Male")
# n1 <- nPlot(Freq ~ Hair, group = "Eye", data = hair_eye_male, type = "multiBarChart")
# n1$print("chart3")


## M <- gvisMotionChart(timesbymonth, 'LeadTime', 'Year',
##       options=list(width=400, height=350))
## plot(M)

```

## Control Charts
### All Incident Types : Lead Time

```{r, echo=FALSE}

kanban <- kanban[order(as.Date(kanban$Closed, format="%Y-%m-%d")),]


#Fixed Delivery Date Service Class
kanban.fixeddeliverydate <- subset(kanban, !is.na(kanban$Due.Date))
#Fixed Delivery Date Service Class
kanban.nodeliverydate <- subset(kanban, is.na(kanban$Due.Date))
#kanban.features is also the Standard Service Class
kanban.features <- subset(kanban, is.na(kanban$Due.Date) & kanban$Type == "Feature")
#kanban.bugs is also the Intangible Service Class
kanban.bugs <- subset(kanban, is.na(kanban$Due.Date) & kanban$Type == "Bug")

mean.lead.time.nodeliverydate <- mean(kanban.nodeliverydate$LeadTime, na.rm = TRUE)
sd.lead.time.nodeliverydate <- sd(kanban.nodeliverydate$LeadTime, na.rm = TRUE)
ucl.nodeliverydate <- mean.lead.time.nodeliverydate + sd.lead.time.nodeliverydate
lcl.nodeliverydate <- mean.lead.time.nodeliverydate - sd.lead.time.nodeliverydate
if (lcl.nodeliverydate<0) {
  lcl.nodeliverydate = 0
}
```

Upper Control Limit: `r ucl.nodeliverydate`  
Mean Lead Time: `r mean.lead.time.nodeliverydate`
Lower Control Limit: `r lcl.nodeliverydate`  

```{r, echo=FALSE}
# make ReleaseDate an ordered factor (so ggplot2 doesn't sort them)
kanban.nodeliverydate$ReleaseDate <- factor(kanban.nodeliverydate$Closed, levels = kanban.nodeliverydate$Closed, ordered = TRUE)

library(ggplot2)
p <- ggplot(kanban.nodeliverydate, aes(x = Closed, y=LeadTime)) + geom_point(aes(color=factor(kanban.nodeliverydate$Type)))

p + geom_abline(intercept = lcl.nodeliverydate, slope = 0, color="red") + 
    geom_abline(intercept = mean.lead.time.nodeliverydate, slope = 0) +
    geom_abline(intercept = ucl.nodeliverydate, slope = 0, color="red") 

p2 <- ggplot(kanban.nodeliverydate, aes(x = Closed, y=LeadTime)) + geom_point(aes(color=factor(kanban.nodeliverydate$Type)))

 p2 + geom_abline(intercept = lcl.nodeliverydate, slope = 0, color="red") + 
     geom_abline(intercept = mean.lead.time.nodeliverydate, slope = 0) +
     geom_abline(intercept = ucl.nodeliverydate, slope = 0, color="red") 
 
 p2 + facet_grid(. ~ kanban.nodeliverydate$Type)

#use facets to auto gen multiple charts...
```

### Bugs : Lead Time

```{r, echo=FALSE}

mean.lead.time.bugs <- mean(kanban.bugs$LeadTime, na.rm = TRUE)
sd.lead.time.bugs <- sd(kanban.bugs$LeadTime, na.rm = TRUE)
ucl.bugs <- mean.lead.time.bugs + sd.lead.time.bugs
lcl.bugs <- mean.lead.time.bugs - sd.lead.time.bugs

if (lcl.bugs<0) {
  lcl.bugs = 0
}

# make ReleaseDate an ordered factor (so ggplot2 doesn't sort them)
kanban.bugs$Closed <- factor(kanban.bugs$Closed, levels = kanban.bugs$Closed, ordered = TRUE)

p <- ggplot(kanban.bugs, aes(x = Closed, y=LeadTime)) + geom_point()  
p + geom_abline(intercept = lcl.bugs, slope = 0, color="red") + 
    geom_abline(intercept = mean.lead.time.bugs, slope = 0) +
    geom_abline(intercept = ucl.bugs, slope = 0, color="red") 

```

Upper Control Limit: `r ucl.bugs`  
Mean Lead Time: `r mean.lead.time.bugs`  
Lower Control Limit: `r lcl.bugs`  


### Feature : Lead Time

```{r, echo=FALSE}

mean.lead.time.features <- mean(kanban.features$LeadTime, na.rm = TRUE)
sd.lead.time.features <- sd(kanban.features$LeadTime, na.rm = TRUE)
ucl.features <- mean.lead.time.features + sd.lead.time.features
lcl.features <- mean.lead.time.features - sd.lead.time.features

if (lcl.features<0) {
  lcl.features = 0
}

# make ReleaseDate an ordered factor (so ggplot2 doesn't sort them)
kanban.features$Closed <- 
    factor(kanban.features$Closed, levels = 
               kanban.features$Closed, ordered = TRUE)

p <- ggplot(kanban.features, aes(x = Closed, y=LeadTime)) + geom_point()  
p + geom_abline(intercept = lcl.features, slope = 0, color="red") + 
    geom_abline(intercept = mean.lead.time.features, slope = 0) +
    geom_abline(intercept = ucl.features, slope = 0, color="red") 

```

Upper Control Limit: `r ucl.features`  
Mean Lead Time: `r mean.lead.time.features`  
Lower Control Limit: `r lcl.features`  

### Feature : Cycle Time

```{r, echo=FALSE}

mean.cycle.time.features <- mean(kanban.features$CycleTime, na.rm = TRUE)
sd.cycle.time.features <- sd(kanban.features$CycleTime, na.rm = TRUE)
ucl.features <- mean.cycle.time.features + sd.cycle.time.features
lcl.features <- mean.cycle.time.features - sd.cycle.time.features

if (lcl.features<0) {
  lcl.features = 0
}

# make ReleaseDate an ordered factor (so ggplot2 doesn't sort them)
kanban.features$Closed <- 
    factor(kanban.features$Closed, levels = 
               kanban.features$Closed, ordered = TRUE)

p <- ggplot(kanban.features, aes(x = Closed, y=CycleTime)) + geom_point()  
p + geom_abline(intercept = lcl.features, slope = 0, color="red") + 
    geom_abline(intercept = mean.cycle.time.features, slope = 0) +
    geom_abline(intercept = ucl.features, slope = 0, color="red") 

```

Upper Control Limit: `r ucl.features`  
Mean Cycle Time: `r mean.cycle.time.features`  
Lower Control Limit: `r lcl.features`  
